Versatile Robust Clustering of Ad Hoc Cognitive Radio Network

### 2016-04-07 journal-draft/bare_jrnl_comsoc.tex
corrections in the appendix

\begin{itemize}
\item Given a collection $\mathcal{Q}$, on basis of which we construct a CRN.
We prepare $N$ CR nodes who are labelled from 1 to $N$, put them on a 2 dimension space, and deem a pair of them can communicate if they appear in one same set in $\mathcal{Q}$.
We regard each set in $\mathcal{Q}$ is a cluster, whose number of CCCs equals to the weight of that set.

%There is one situation deserving extra explanation in the second transformation, we adopt one example to discuss it.
Assuming two sets in $\mathcal{Q}$ are $s_1=\{1,2\}$ and $s_2=\{1,2,3\}$, then their weights are 3 and 5 respectively.
%Their dummy sets are $s_1'=\{1,1,2,2\}$ and $s_2'=\{1,1,2,2,3,3,4,4\}$ and their new weights are 3 and 5 as before.
We find it is impossible to map the sets into clusters in the same time, because the number of CCCs of the cluster which bases on $s_1$ should be no less than the cluster which bases on $s_2$, as the latter has one extra node compared with the former cluster.
%When $s_1'$ and $s_2'$ are mapped to CRN respectively, there is contradiction between them, because the number of common channels of CR node group $\{1,1,2,2\}$ is smaller than that of $\{1,1,2,2,3,3,4,4\}$.
But as to any instance of the solution to the weighted k-set packing problem, this contradiction doesn't happen because the instance $\mathcal{S}$ contains only disjoint sets, thus at most only one set of $s_1$ and $s_2$ appears in $\mathcal{S}$.%, then we can safely delete the connections based on the deleted set from the CRN, and the contradiction is eliminated.

\item In the second step, we transform the instance $\mathcal{S}$ to $\mathcal{S'}$ by adding dummy elements into each set in $\mathcal{S}$.
For each set $s_i\in \mathcal{S}$, the elements in $s_i$ are duplicated, for instance, given $s_i=\{1, 4, 6\}$, the dummy set $s_i'$ is $\{1,1,4,4,6,6\}$.
%By doing this, we obtain the dummy sets and constitute the dummy instance $\mathcal{S}'$ based on $\mathcal{S}$.
The purpose of this transformation is to eliminate the set in $\mathcal{S}$, which has single element.
The weight of set is unchanged after this transformation, \ie $\omega(s_i)=\omega(s_i')$.
%After this transmission, there is no set with only one element.
This transformation requires $\sum_{s_i \in \mathcal{S}} |s_i|$ steps.

\item In this step, we transform the instance $\mathcal{S'}$ to a clustering solution for CRN.
We prepare a second pool of CR nodes which are identical with the CR nodes prepared in step 1, i.e., identical IDs and channel availabilities on them, we call these CR nodes as dummy nodes.
We locate these CR nodes besides the CR nodes with the sane IDs in the CRN built in step 1, and there is connection between the CR node and its dummy node (the one CR node and its dummy node can be seen as two transceivers at one node).
Because of the dummy nodes, the clustering solution which corresponds to $\mathcal{S'}$ doesn't have singleton cluster.
This transformation requires $2\cdot\sum_{s_i \in \mathcal{S}} |s_i|$ steps.
%
Afterwards, the CR node whose ID doesn't appear in any set in $\mathcal{S}$ becomes single node clusters, according to the definition of clustering problem in CRN, the number of CCCs in these single node clusters is 0.
These singleton clusters and the clusters in $\mathcal{S}$ constitute a clustering solution, and finding the singleton clusters requires at most $N$ steps.
%We deliberately locate them so that at least one CR node can communicate with the rest of them.
%map every element in $\mathcal{S}$ into one CR node, \ie each integer corresponds to one CR node, in particular, that integer becomes the CR node's ID.
%As $s'$ is dummy set which has duplicated elements, we also deploy the the same CR node twice.
%
An example is shown in Table~\ref{no_hard_proof_instance}.
\begin{table}[h!]
     \begin{center}
     \begin{tabular}{ p{3cm}  p{4.5cm} }
     \toprule
      $\mathcal{N}$  & $\{1,2,3,4,5\}$\\ 
    \cmidrule(r){1-1}\cmidrule(lr){2-2}     
      $\mathcal{Q}$  & $\{(1),(1, 5),(1,2,4),(2,3), (4)\}$\\ 
    \cmidrule(r){1-1}\cmidrule(lr){2-2}     
      Instance for Weighted k-set packing  & $\{(1),(2,3), (4)\}$\\ 
    \cmidrule(r){1-1}\cmidrule(lr){2-2}
      Instance with dummy elements
      & 
		$\{(1,1),(2,2,3,3), (4,4)\}$
      \\    \cmidrule(r){1-1}\cmidrule(lr){2-2}
	Instance for clustering solution (dashed circles are dummy nodes)
	  &
	  %\raisebox{-\totalheight}{\includegraphics[width=0.8\linewidth]{np_hard_proof_dummy.pdf}}      
	  \begin{minipage}{.3\textwidth}
      \includegraphics[width=0.8\linewidth]{np_hard_proof_dummy.pdf}
    \end{minipage}
	  \\       \bottomrule
      \end{tabular}
      \caption{}
      \label{no_hard_proof_instance}
      \end{center}
      \end{table}

>>>>

\begin{itemize}
\item Given a collection $\mathcal{Q}$, on basis of which we construct a CRN. (I DON'T UNDERSTAND THAT. What do you mean?)
%We prepare $N$ CR nodes who are labelled from 1 to $N$, put them on a 2 dimension space, and deem a pair of them can communicate if they appear in one same set in $\mathcal{Q}$.
We define a set of CR nodes $\mathcal{N} = \{ 1, \ldots , N \}$
We regard each set in $\mathcal{Q}$ as a cluster, whose number of CCCs is equal to the weight of that set.

%There is one situation deserving extra explanation in the second transformation, we adopt one example to discuss it.
Assuming two sets in $\mathcal{Q}$ are $s_1=\{1,2\}$ and $s_2=\{1,2,3\}$, then their weights are 3 and 5 respectively. (THAT'S TOO HAND-WAVY.)
%Their dummy sets are $s_1'=\{1,1,2,2\}$ and $s_2'=\{1,1,2,2,3,3,4,4\}$ and their new weights are 3 and 5 as before.
We find it is impossible to map the sets into clusters in the same time (SORRY, which sets?? The sets you mentioned before are already clusters, isn't it?), because the number of CCCs of the cluster which bases on $s_1$ should be no less than the cluster which bases on $s_2$, as the latter has one extra node compared with the former cluster.
%When $s_1'$ and $s_2'$ are mapped to CRN respectively, there is contradiction between them, because the number of common channels of CR node group $\{1,1,2,2\}$ is smaller than that of $\{1,1,2,2,3,3,4,4\}$.
But as to any instance of the solution to the weighted k-set packing problem, this contradiction doesn't happen because the instance $\mathcal{S}$ contains only disjoint sets, thus at most only one set of $s_1$ and $s_2$ appears in $\mathcal{S}$.%, then we can safely delete the connections based on the deleted set from the CRN, and the contradiction is eliminated.
(THIS PARAGRAPH IS TOO DIFFICULT FOR ME TO UNDERSTAND.)

\item In the second step, we transform the instance $\mathcal{S}$ to $\mathcal{S'}$ by adding dummy elements into each set in $\mathcal{S}$.
Formally, for each set $s_i\in \mathcal{S}$, we create $s_i' = s_i \times \{ 1,2\}$. %for instance, given $s_i=\{1, 4, 6\}$, the dummy set $s_i'$ is $\{1,1',4,4',6,6' \}$.
%By doing this, we obtain the dummy sets and constitute the dummy instance $\mathcal{S}'$ based on $\mathcal{S}$.
The purpose of this transformation is to eliminate the set in $\mathcal{S}$, which has single element.
The weight of these sets remain unchanged, \ie $\omega(s_i)=\omega(s_i')$.
%After this transmission, there is no set with only one element.
%This transformation requires $\sum_{s_i \in \mathcal{S}} |s_i|$ steps.

\item In this step, we transform the instance $\mathcal{S'}$ to a clustering solution for CRN.
We prepare a second pool of CR nodes which are identical with the CR nodes prepared in step 1, i.e., identical IDs and channel availabilities on them, we call these CR nodes dummy nodes.
We locate these CR nodes besides the CR nodes with the same IDs (THAT DOESN'T MAKE SENSE. THEN THE ID IS NOT UNIQUE ANYMORE.) in the CRN built in step 1, and there is connection between the CR node and its dummy node (the one CR node and its dummy node can be seen as two transceivers at one node). (YOU DON'T NEED TO GIVE PRACTICAL MOTIVATION IN A HARDNESS-PROOF.)
Because of the dummy nodes, the clustering solution which corresponds to $\mathcal{S'}$ doesn't have singleton cluster.
This transformation requires $2\cdot\sum_{s_i \in \mathcal{S}} |s_i|$ steps.
%
Afterwards, the CR node whose ID doesn't appear in any set in $\mathcal{S}$ becomes single node clusters, according to the definition of clustering problem in CRN, the number of CCCs in these single node clusters is 0.
These singleton clusters and the clusters in $\mathcal{S}$ constitute a clustering solution, and finding the singleton clusters requires at most $N$ steps.
%We deliberately locate them so that at least one CR node can communicate with the rest of them.
%map every element in $\mathcal{S}$ into one CR node, \ie each integer corresponds to one CR node, in particular, that integer becomes the CR node's ID.
%As $s'$ is dummy set which has duplicated elements, we also deploy the the same CR node twice.
%
An example is shown in Table~\ref{no_hard_proof_instance}.
\begin{table}[h!]
     \begin{center}
     \begin{tabular}{ p{3cm}  p{4.5cm} }
     \toprule
      $\mathcal{N}$  & $\{1,2,3,4,5\}$\\ 
    \cmidrule(r){1-1}\cmidrule(lr){2-2}     
      $\mathcal{Q}$  & $\{ \{1\}, \{1, 5\}, \{1,2,4\}, \{2,3\}, \{4\} \}$\\ 
    \cmidrule(r){1-1}\cmidrule(lr){2-2}     
      Instance for Weighted k-set packing  & $\{ \{1\}, \{2,3\}, \{4\} \}$\\ 
    \cmidrule(r){1-1}\cmidrule(lr){2-2}
      Instance with dummy elements
      & 
		$\{ \, \{(1,1),(1,2)\},\{(2,1),(2,2),$ \\ &$(3,1),(3,2) \}, \{ (4,1), (4,2) \} \, \}$
      \\    \cmidrule(r){1-1}\cmidrule(lr){2-2}
	Instance for clustering solution (dashed circles are dummy nodes)
	  &
	  %\raisebox{-\totalheight}{\includegraphics[width=0.8\linewidth]{np_hard_proof_dummy.pdf}}      
	  \begin{minipage}{.3\textwidth}
      \includegraphics[width=0.8\linewidth]{np_hard_proof_dummy.pdf}
    \end{minipage}
	  \\       \bottomrule
      \end{tabular}
      \caption{}
      \label{no_hard_proof_instance}
      \end{center}
      \end{table}
